Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-21 paper/ms.tex
discussion in terms of abundance matching

\subsection{Models in the context of abundance matching}

The abundance matching methods, whereby a stellar mass is associated
to a halo mass in order to reproduce various luminosity functions, can
be used to interpret the results we have obtained so far.

In the case of a narrow of masses to host LAEs the upper masses are
bound to be $M_{\rm max}< 10^{11.5}$\hMsun as it is show in Figure
\ref{figure:mock_and_f_occ}. For halos more massive than this bound it
is naturally expected that the galaxies can be observed as Lyman Break
Galaxies (LBGs). This would imply that not all the bright LBGs can
detected as a LAE.

>>>>

\subsection{In the context of abundance matching models}

Using abundance matching methods throughout cosmic time from redshifts
$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
formation efficiency (star formation rate divided by the stellar mass)
presents a clear maximum around $10^{11.7}$\Msun at all redshifts
$z<4$.

This mass scale is strictly superior to the all the $M_{\rm max}$
values allowed in the consistent models. Using the results published
in \cite{Behroozi2013a} we find that the typical stellar mass in halos
of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
their star formion rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$. These halo
masses actually correspond to the lower bound of what is computed in
the abundance matching model in order to fit the observational data
for the stellar mass function.
